---
title: "Black Bear Code (noint)"
author: "Kelly Bruno"
date: '2022-09-24'
output:
  pdf_document: 
    latex_engine: lualatex
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

##set working directory
setwd("~/Black Bears")

# Clear Environment and Load Packages -------------------------------------

rm(list = ls())
library(AER)
library(arm)
library(Sleuth3)
library(lmerTest)
library(tidyverse)
library(GGally) #check assumptions
library(ggplot2) #graphing
library(AICcmodavg) #AIC tables
library(usdm) #for VIF calculations on dataframe
library(lme4) #for assumption tests in mixed effects model
library(gridExtra) #grid for plots
library(sjPlot) #visualizing mixed-effects models
library(sjstats) #ICC - intraclass-correlation coefficent
require(jtools) ##plots and saving plots
library(viridis) #color scheme
theme_set(theme_classic(12))

##load data
load(file = "Luna_pace.RData")

```

#######################
#######################
## Luna Pace Model   ##
#######################
#######################

#Data exploration

```{r}

##remove october data
luna_pace <- luna_pace[!(luna_pace$Month == "10"),]

##check distribution of hours (needs grouping)
xtabs(~Pace + Hour, data = luna_pace)
luna_pace$Hour_group <- ifelse(luna_pace$Hour %in% c(9, 10, 11), "Morning",
                               ifelse(luna_pace$Hour %in% c(12, 13), "Mid-day",
                                      ifelse(luna_pace$Hour %in% c(14, 15, 16), "Afternoon", "")))

xtabs(~Pace + Hour_group, data = luna_pace)

##as factor
luna_pace$Hour_group <- as.factor(luna_pace$Hour_group)

##now access (fine)
xtabs(~Pace + Access, data = luna_pace)

##explore the data
head(luna_pace)

#check structure
str(luna_pace)

#USE A BOXPLOT/TABLE/FIND DESCRIPTIVE STATS to EXPLORE FACTORS (YOU DID SOMETHING SIMILAR BELOW BUT THE NUMBERS HERE ARE HELPFUL TO ME)
apply(table(luna_pace[, c("Pace", "Access")]), 1, prop.table)
apply(table(luna_pace[, c("Pace", "Season")]), 1, prop.table)
apply(table(luna_pace[, c("Pace", "Hour_group")]), 1, prop.table)

##plot of data
##access seems to negatively effect pacing
ggplot(luna_pace, aes(x = Access, y = Pace)) +
  stat_summary(fun.data = mean_cl_boot,size = 0.5)+
  ylim(c(0,1))

##time of day seems to effect pacing
ggplot(luna_pace, aes(x = Hour_group, y = Pace)) +
  stat_summary(fun.data = mean_cl_boot,size = 0.5)+
  ylim(c(0,1))

#PACE SHOULD BE A FACTOR NOW! No numerical meaning to the 0,1
luna_pace$Pace <- factor(luna_pace$Pace)

```

##################
##Start modeling##
##################

```{r}

#MAKE YOUR MODELS WHICH REFLECT PREDICTIONS

modlist<-list()

modlist[["full"]] <- full <- glm(Pace ~ Access + Season + Hour_group, data = luna_pace, family = "binomial")

modlist[["null"]]<-null <- glm(Pace ~ 1, data = luna_pace, family = "binomial")

modlist[["access.season"]] <- as <- glm(Pace ~ Access + Season, data = luna_pace, family = "binomial")

modlist[["access.hour"]] <- ah <- glm(Pace ~ Access + Hour_group, data = luna_pace, family = "binomial")

modlist[["access"]]<- a <- glm(Pace ~ Access, data = luna_pace, family = "binomial")

modlist[["hour"]]<-h <- glm(Pace ~ Hour_group, data = luna_pace, family = "binomial")

modlist[["season"]]<- s <- glm(Pace ~ Season, data = luna_pace, family = "binomial")

modlist[["hour.season"]] <- hs <- glm(Pace ~ Hour_group + Season, data = luna_pace, family = "binomial")

#COMPARE YOUR AICS#

aictab(modlist)

#THE FULL MODEL IS THE BEST! LET'S EXPLORE MAKING SEASON A RANDOM EFFECT  BECAUSE WE SUSPECTED IT WOULD NEED TO BE CONTROLLED FOR

modlist1 <- list()


modlist1[["null"]] <- null <- glmer(Pace ~ 1 + (1|Season), data = luna_pace, family = "binomial")

modlist1[["full"]] <- full <- glmer(Pace ~ Access + Hour_group + (1|Season), data = luna_pace, family = "binomial")

modlist1[["access"]] <- a <- glmer(Pace ~ Access + (1|Season), data = luna_pace, family = "binomial")

modlist1[["hour"]] <- h <- glmer(Pace ~ Hour_group + (1|Season), data = luna_pace, family = "binomial")

aictab(modlist1)
#full model is best

```

###############
##Final Model##
###############

```{r}

summary(full)
tab_model(full)
##Marginal R^2 - 0.218 and Conditional R^2 - 0.298

##unique probabilities
probs_luna_pace <- unique(fitted(full))
probs_luna_pace

probl_pace <- unique(predict(full, type="response"))

##best model is full model with season as random variable

```

####################
##Test Assumptions##
####################

```{r}
#pull coefficients
co_lunapace <- fixef(full)
co_lunapace

###over fitting
isSingular(full)
#False, no overfitting

```

###################
##Plot the Model ##
###################

```{r}

##model with response = pace, predictors = access and hour groups and season as random variable
plot_model(full, type = "pred", terms = c("Hour_group"))
plot_model(full, type = "pred", terms = c("Access"))

##basic effects plot
require(effects)
plot (allEffects(full))


###prepare plot
newdata <- expand.grid(Access = c("No","Yes"),
Season = c("Non-Denning", "Denning"))
fit <- data.frame(x = predict(a, newdata = newdata, se.fit = F, type = "response"))
access <- data.frame(newdata, Pace = fit$x)
access1 <- access %>% group_by(Access) %>% summarise(mn = mean(Pace, na.rm = T), se = sd(Pace, na.rm = T)/sqrt(n()))

#plot
pdatfull <- mutate(access1, labs = c("Limited Access", "Full Access"))

jpeg(file="luna_pace_fin.jpeg")
p <- ggplot(pdatfull, aes(x = labs, y = mn)) + 
  geom_line(size = 2) +                 
  geom_col(data = pdatfull, aes(x = labs, y = mn, group = NULL),
           size = 1, position = position_dodge(width = 0.8), fill = c("lightsteelblue", "firebrick")) + 
  geom_errorbar(data = pdatfull, aes(x = labs, y = mn, ymax = mn + se, 
                                    ymin = mn - se, group = NULL), width = 0.2, position = position_dodge(width = 0.8)) +
  labs(y = "Predicted likelihood of pacing", x = "Access Type") +
  theme_bw(base_size = 30) +
  theme(text = element_text(size=15))
p + theme(legend.background = element_rect(size=0.5, linetype="solid", 
                                           colour ="black"))+ theme(legend.position = c(0.2, .9))
dev.off()


##points
jpeg(file="luna_pace_point.jpeg")
p1 <- ggplot(pdatfull, aes(x = labs, y = mn, color = Access,)) + 
  geom_line(size = 3) +                 
  geom_point(data = pdatfull, aes(x = labs, y = mn, color = Access, group = NULL, size = 2),
           size = 1, position = position_dodge(width = 0.8)) + 
  geom_errorbar(data = pdatfull, aes(x = labs, y = mn, ymax = mn + se, 
                                    ymin = mn - se, group = NULL), width = 0.2, position = position_dodge(width = 0.8)) +
  scale_color_manual(name = NULL, labels = c("Limited Access", "Full Access"), 
                    values = c("lightsteelblue", "firebrick")) +
  labs(y = "Predicted likelihood of pacing", x = "Access Type") +
  theme_bw(base_size = 30) +
  theme(text = element_text(size=15))
p1 + theme(legend.background = element_rect(size=0.5, linetype="solid", 
                                           color ="black"))+ theme(legend.position = c(0.2, .9))



pdatfull
p
p1

```


```{r}

#access probs
newdata <- expand.grid(Access = c("No","Yes"),
Season = c("Non-Denning", "Denning"))
fit <- data.frame(x = predict(a, newdata = newdata, se.fit = F, type = "response"))
access <- data.frame(newdata, Pace = fit$x)
access1 <- access %>% group_by(Access) %>% summarise(mn = mean(Pace, na.rm = T), se = sd(Pace, na.rm = T)/sqrt(n()))
#No
#0.3303017
#SD 0.13611412

#Yes
#0.1112120
#SD 0.05803405


#hour probs
newdata <- expand.grid(Hour_group = c("Morning","Mid-day", "Afternoon"),
Season = c("Non-Denning", "Denning"))
fit <- data.frame(x = predict(h, newdata = newdata, se.fit = F, type = "response"))
hour <- data.frame(newdata, Pace = fit$x)
hour1 <- hour %>% group_by(Hour_group) %>% summarise(mn = mean(Pace, na.rm = T), se = sd(Pace, na.rm = T)/sqrt(n()))
#Morning 0.05377721
#Mid-day 0.15783898
#afternoon 0.24000000

```

#######################
#######################
## Nova Pace Model   ##
#######################
#######################

```{r}
##set working directory
setwd("~/Black Bears")

#remove previous data
##run libraries again
rm(list = ls())
library(AER)
library(arm)
library(Sleuth3)
library(lmerTest)
library(tidyverse)
library(GGally) #check assumptions
library(ggplot2) #graphing
library(AICcmodavg) #AIC tables
library(usdm) #for VIF calculations on dataframe
library(lme4) #for assumption tests in mixed effects model
library(gridExtra) #grid for plots
library(sjPlot) #visualizing mixed-effects models
library(sjstats) #ICC - intraclass-correlation coefficent
require(jtools) ##plots and saving plots
library(viridis) #color scheme
theme_set(theme_classic(12))

##load data
load(file = "Nova_pace.RData")


```

#Date Exploration

```{r}

##remove october data
nova_pace <- nova_pace[!(nova_pace$Month == "10"),]

##check distribution of hours (needs grouping)
xtabs(~Pace + Hour, data = nova_pace)


nova_pace$Hour_group <- ifelse(nova_pace$Hour %in% c(9, 10, 11), "Morning",
                               ifelse(nova_pace$Hour %in% c(12, 13), "Mid-day",
                                      ifelse(nova_pace$Hour %in% c(14, 15, 16), "Afternoon", "")))
xtabs(~Pace + Hour_group, data = nova_pace)

##as factor
nova_pace$Hour_group <- as.factor(nova_pace$Hour_group)

##now access (fine)
xtabs(~Pace + Access, data = nova_pace)

##explore the data
head(nova_pace)
str(nova_pace)

#USE A BOXPLOT/TABLE/FIND DESCRIPTIVE STATS to EXPLORE FACTORS
apply(table(nova_pace[, c("Pace", "Access")]), 1, prop.table)
apply(table(nova_pace[, c("Pace", "Season")]), 1, prop.table)
apply(table(nova_pace[, c("Pace", "Hour_group")]), 1, prop.table)

##plot of data
##access seems to have small effect on foraging
ggplot(nova_pace, aes(x = Access, y = Pace)) +
  stat_summary(fun.data = mean_cl_boot,size = 0.5)+
  ylim(c(0,1))

##no clear relationship between hour of day and foraging
ggplot(nova_pace, aes(x = Hour_group, y = Pace)) +
  stat_summary(fun.data = mean_cl_boot,size = 0.5)+
  ylim(c(0,1))


#PACE SHOULD BE A FACTOR NOW
nova_pace$Pace <- factor(nova_pace$Pace)

```

##################
##Start modeling##
##################

```{r}

#Models

modlist <- list()


modlist[["null"]] <- null <- glmer(Pace ~ 1 + (1|Season), data = nova_pace, family = "binomial")

modlist[["full"]] <- full <- glmer(Pace ~ Hour_group + Access + (1|Season), data = nova_pace, family = "binomial")

modlist[["access"]] <- a <- glmer(Pace ~ Access + (1|Season), data = nova_pace, family = "binomial")

modlist[["hour"]] <- h <- glmer(Pace ~ Hour_group + (1|Season), data = nova_pace, family = "binomial")

#compare AICs
aictab(modlist)

#full model is best

```

###############
##Final Model##
###############

```{r}

##full model best
summary(full)

tab_model(full)
##Marginal R^2 - 0.121 and Conditional R^2 - 0.806
##nova appears to be more impacted by seasonality than luna or we are missing
#some important variable for luna

```

####################
##Test Assumptions##
####################

```{r}

#pull coefficients
co_novapace <- fixef(full)
co_novapace

###over fitting
isSingular(full)
#False, no overfitting

```

###################
##Plot the Model ##
###################

```{r}

##model with response = pace, predictors = access and hour groups and season as random variable
plot_model(full, type = "pred", terms = c("Access", "Hour_group"))

##basic effects plot
require(effects)
plot (allEffects(full))


###prepare plot
newdata <- expand.grid(Access = c("No","Yes"),
Season = c("Non-Denning", "Denning"))
fit <- data.frame(x = predict(a, newdata = newdata, se.fit = F, type = "response"))
access <- data.frame(newdata, Pace = fit$x)
access1 <- access %>% group_by(Access) %>% summarise(mn = mean(Pace, na.rm = T), se = sd(Pace, na.rm = T)/sqrt(n()))

#plot
pdatfull <- mutate(access1, labs = c("Limited Access", "Full Access"))

jpeg(file="nova_pace_fin.jpeg")
p <- ggplot(pdatfull, aes(x = labs, y = mn)) + 
  geom_line(size = 2) +                 
  geom_col(data = pdatfull, aes(x = labs, y = mn, group = NULL),
           size = 1, position = position_dodge(width = 0.8), fill = c("lightsteelblue", "firebrick")) + 
  geom_errorbar(data = pdatfull, aes(x = labs, y = mn, ymax = mn + se, 
                                    ymin = mn - se, group = NULL), width = 0.2, position = position_dodge(width = 0.8)) +
  labs(y = "Predicted likelihood of pacing", x = "Access Type") +
  theme_bw(base_size = 30) +
  theme(text = element_text(size=15))
p + theme(legend.background = element_rect(size=0.5, linetype="solid", 
                                           colour ="black"))+ theme(legend.position = c(0.2, .9))
dev.off()

p


```


```{r}
#access
#No
#0.07099455
#SD 0.07005064

Yes
#0.02011071
#SD 0.01987114

#hour
newdata <- expand.grid(Hour_group = c("Morning","Mid-day", "Afternoon"),
Season = c("Non-Denning", "Denning"))
fit <- data.frame(x = predict(h, newdata = newdata, se.fit = F, type = "response"))
hour <- data.frame(newdata, Pace = fit$x)
hour1 <- hour %>% group_by(Hour_group) %>% summarise(mn = mean(Pace, na.rm = T), se = sd(Pace, na.rm = T)/sqrt(n()))
#Morning
#0.007985841
#SD 0.007963842

#Mid-day
#0.036026905
#SD 0.035921691

#Afternoon
#0.120256203
#SD 0.119827576
```

#######################
#######################
## Luna Forage Model ##
#######################
#######################

```{r}
##set working directory
setwd("~/Black Bears")

#remove previous data
rm(list = ls())
##run libraries again
library(AER)
library(arm)
library(Sleuth3)
library(lmerTest)
library(tidyverse)
library(GGally) #check assumptions
library(ggplot2) #graphing
library(AICcmodavg) #AIC tables
library(usdm) #for VIF calculations on dataframe
library(lme4) #for assumption tests in mixed effects model
library(gridExtra) #grid for plots
library(sjPlot) #visualizing mixed-effects models
library(sjstats) #ICC - intraclass-correlation coefficent
require(jtools) ##plots and saving plots
library(viridis) #color scheme
theme_set(theme_classic(12))

#load data
load(file = "Luna_forage.RData")

##remove october data
luna_forage <- luna_forage[!(luna_forage$Month == "10"),]


```

#Data exploration

```{r}

#check distribution of hours (needs grouping)
xtabs(~Foraging + Hour, data = luna_forage)
luna_forage$Hour_group <- ifelse(luna_forage$Hour %in% c(9, 10, 11), "Morning",
                                 ifelse(luna_forage$Hour %in% c(12, 13), "Mid-day",
                                        ifelse(luna_forage$Hour %in% c(14, 15, 16), "Afternoon", "")))
xtabs(~Foraging + Hour_group, data = luna_forage)

##as factor
luna_forage$Hour_group <- as.factor(luna_forage$Hour_group)

##now access (fine)
xtabs(~Foraging + Access, data = luna_forage)

##explore the data
head(luna_forage)
str(luna_forage)

#USE A BOXPLOT/TABLE/FIND DESCRIPTIVE STATS to EXPLORE FACTORS
apply(table(luna_forage[, c("Foraging", "Access")]), 1, prop.table)
apply(table(luna_forage[, c("Foraging", "Season")]), 1, prop.table)
apply(table(luna_forage[, c("Foraging", "Hour_group")]), 1, prop.table)

##plot of data
##access seems to have an effect on foraging
ggplot(luna_forage, aes(x = Access, y = Foraging)) +
  stat_summary(fun.data = mean_cl_boot,size = 0.5)+
  ylim(c(0,1))

##some effect of time of day on foraging
ggplot(luna_forage, aes(x = Hour_group, y = Foraging)) +
  stat_summary(fun.data = mean_cl_boot,size = 0.5)+
  ylim(c(0,1))

#FORAGE SHOULD BE A FACTOR NOW
luna_forage$Foraging <- factor(luna_forage$Foraging)

```

##################
##Start modeling##
##################

```{r}

#Models

modlist <- list()


modlist[["null"]] <- null <- glmer(Foraging ~ 1 + (1|Season), data = luna_forage, family = "binomial")

modlist[["full"]] <- full <- glmer(Foraging ~ Access + Hour_group + (1|Season), data = luna_forage, family = "binomial")

modlist[["access"]] <- a <- glmer(Foraging ~ Access + (1|Season), data = luna_forage, family = "binomial")

modlist[["hour"]] <- h <- glmer(Foraging ~ Hour_group + (1|Season), data = luna_forage, family = "binomial")

#compare AICs
aictab(modlist)
#access model best by >2 compared to full

```

#Final Model

```{r}

##summarize model, access best model
summary(a)
tab_model(a)
##Marginal R^2 - 0.014 and Conditional R^2 - 0.074

```

####################
##Test Assumptions##
####################

```{r}

#pull coefficients
co_lunaforage <- fixef(a)
co_lunaforage

###over fitting
isSingular(a)
#False, no overfitting

```

###################
##Plot the Model ##
###################

```{r}

##model with response = pace, predictors = access and hour groups and season as random variable
plot_model(a, type = "pred", terms = c("Access"))

##basic effects plot
require(effects)
plot (allEffects(a))

###prepare plot
pred_data <- expand.grid(Access = c("No","Yes"),
                         Season = c("Non-Denning", "Denning"))
fit <- data.frame(x = predict(a, newdata = pred_data, se.fit = F, type = "response"))
pdat1 <- data.frame(pred_data, Foraging = fit$x)
pdata <- pdat1 %>% group_by(Access) %>% summarise(mn = mean(Foraging, na.rm = T), se = sd(Foraging, na.rm = T)/sqrt(n()))

#plot

pdata <- mutate(pdata, labs = c("Limited Access", "Full Access"))

jpeg(file="luna_forage_fin.jpeg")
p <- ggplot(pdata, aes(x = labs, y = mn)) + 
  geom_line(size = 2) +                 
  geom_col(data = pdata, aes(x = labs, y = mn, group = NULL),
           size = 1, position = position_dodge(width = 0.8), fill = c("lightsteelblue", "firebrick")) + 
  geom_errorbar(data = pdata, aes(x = labs, y = mn, ymax = mn + se, 
                                    ymin = mn - se, group = NULL), width = 0.2, position = position_dodge(width = 0.8)) +
  labs(y = "Predicted likelihood of foraging", x = "Access Type") +
  theme_bw(base_size = 30) +
  theme(text = element_text(size=15))
p + theme(legend.background = element_rect(size=0.5, linetype="solid", 
                                           colour ="black"))+ theme(legend.position = c(0.2, .9))
dev.off()

pdata
p

```

#######################
#######################
## Nova Forage Model ##
#######################
#######################

```{r}

##set working directory
setwd("~/Black Bears")

#remove previous data
rm(list = ls())
##run libraries again
library(AER)
library(arm)
library(Sleuth3)
library(lmerTest)
library(tidyverse)
library(GGally) #check assumptions
library(ggplot2) #graphing
library(AICcmodavg) #AIC tables
library(usdm) #for VIF calculations on dataframe
library(lme4) #for assumption tests in mixed effects model
library(gridExtra) #grid for plots
library(sjPlot) #visualizing mixed-effects models
library(sjstats) #ICC - intraclass-correlation coefficent
require(jtools) ##plots and saving plots
library(viridis) #color scheme
theme_set(theme_classic(12))

##load data
load(file = "Nova_forage.RData")

##remove october data
nova_forage <- nova_forage[!(nova_forage$Month == "10"),]


```

#data exploration

```{r}
##check distribution of hours (needs grouping)
xtabs(~Foraging + Hour, data = nova_forage)


nova_forage$Hour_group <- ifelse(nova_forage$Hour %in% c(9, 10, 11), "Morning",
                                 ifelse(nova_forage$Hour %in% c(12, 13), "Mid-day",
                                        ifelse(nova_forage$Hour %in% c(14, 15, 16), "Afternoon", "")))
xtabs(~Foraging + Hour_group, data = nova_forage)

##as factor
nova_forage$Hour_group <- as.factor(nova_forage$Hour_group)

##now access (fine)
xtabs(~Foraging + Access, data = nova_forage)

##explore the data
head(nova_forage)
str(nova_forage)

#USE A BOXPLOT/TABLE/FIND DESCRIPTIVE STATS to EXPLORE FACTORS
apply(table(nova_forage[, c("Foraging", "Access")]), 1, prop.table)
apply(table(nova_forage[, c("Foraging", "Season")]), 1, prop.table)
apply(table(nova_forage[, c("Foraging", "Hour_group")]), 1, prop.table)

##plot of data
##hard to see an effect of access on foraging here
ggplot(nova_forage, aes(x = Access, y = Foraging)) +
  stat_summary(fun.data = mean_cl_boot,size = 0.5)+
  ylim(c(0,1))

##no clear relationship between time of day and foraging
ggplot(nova_forage, aes(x = Hour_group, y = Foraging)) +
  stat_summary(fun.data = mean_cl_boot,size = 0.5)+
  ylim(c(0,1))

#Forage SHOULD BE A FACTOR NOW
nova_forage$Foraging <- factor(nova_forage$Foraging)

```

##################
##Start modeling##
##################

```{r}

#Models

modlist <- list()

modlist[["null"]] <- null <- glmer(Foraging ~ 1 + (1|Season), data = nova_forage, family = "binomial")

modlist[["full"]] <- full <- glmer(Foraging ~ Access + Hour_group + (1|Season), data = nova_forage, family = "binomial")

modlist[["access"]] <- a <- glmer(Foraging ~ Access + (1|Season), data = nova_forage, family = "binomial")

modlist[["hour"]] <- h <- glmer(Foraging ~ Hour_group + (1|Season), data = nova_forage, family = "binomial")

#compare AICs
aictab(modlist)
#full model is best

```

#Final model

```{r}

##interaction model best
summary(full)
tab_model(full)
##Marginal R^2 - 0.016 and Conditional R^2 - 0.099

```

####################
##Test Assumptions##
####################

```{r}

#pull coefficients
co_novaforage <- fixef(full)
co_novaforage

###over fitting
isSingular(full)
#False, no overfitting

```

###################
##Plot the Model ##
###################

```{r}

plot_model(full, type = "pred", terms = c("Access", "Hour_group"))

##basic effects plot
require(effects)
plot (allEffects(full))

###prepare plot
newdata <- expand.grid(Access = c("No","Yes"),
Season = c("Non-Denning", "Denning"))
fit <- data.frame(x = predict(a, newdata = newdata, se.fit = F, type = "response"))
access <- data.frame(newdata, Foraging = fit$x)
access1 <- access %>% group_by(Access) %>% summarise(mn = mean(Foraging, na.rm = T), se = sd(Foraging, na.rm = T)/sqrt(n()))

#plot
pdatfull <- mutate(access1, labs = c("Limited Access", "Full Access"))

jpeg(file="nova_forage_fin.jpeg")
p <- ggplot(pdatfull, aes(x = labs, y = mn)) + 
  geom_line(size = 2) +                 
  geom_col(data = pdatfull, aes(x = labs, y = mn, group = NULL),
           size = 1, position = position_dodge(width = 0.8), fill = c("lightsteelblue", "firebrick")) + 
  geom_errorbar(data = pdatfull, aes(x = labs, y = mn, ymax = mn + se, 
                                    ymin = mn - se, group = NULL), width = 0.2, position = position_dodge(width = 0.8)) +
  labs(y = "Predicted likelihood of foraging", x = "Access Type") +
  theme_bw(base_size = 30) +
  theme(text = element_text(size=15))
p + theme(legend.background = element_rect(size=0.5, linetype="solid", 
                                           colour ="black"))+ theme(legend.position = c(0.2, .9))
dev.off()

pdatfull
p

```

```{r}
#access
#No
#0.1046419
#SD 0.04683933

#Yes
#0.1337054
#SD 0.05823779

#hour
newdata <- expand.grid(Hour_group = c("Morning","Mid-day", "Afternoon"),
Season = c("Non-Denning", "Denning"))
fit <- data.frame(x = predict(h, newdata = newdata, se.fit = F, type = "response"))
hour <- data.frame(newdata, Foraging = fit$x)
hour1 <- hour %>% group_by(Hour_group) %>% summarise(mn = mean(Foraging, na.rm = T), se = sd(Foraging, na.rm = T)/sqrt(n()))

#Morning
#0.09721349
#SD 0.03758125

#Mid-day
#0.12697528
#SD 0.04767453

#Afternoon
#0.14787407
#SD 0.05434816

```

